---
title: "How Shifting Priorities and Capacity Affect Policy Work and Constituency Service: Evidence from a Census of Legislator Requests to U.S. Federal Agencies"
author: Devin Judge-Lord, Eleanor Neff Powell, Justin Grimmer
format: md
bibliography: "assets/congress2019.bib"
---

```{r echo=FALSE, results = 'hide'}
# make txt version for dataverse 
file.copy("readme.md", "readme.txt", overwrite = T)
```

# Instructions for replication 

1. Save all files and folders from this dataverse project to the root-level of a project directory and ensure it is the active directory in R. This allows the `here` package to construct valid file paths.
1. run "replication.qmd" to generate all figures and results
1. run "corr.qmd" to render manuscript pdf ("corr.pdf")
1. run "si.qumd" to render Supplemental Information pdf ("si.pdf")

Alternatively to step 2, if you only wish to reproduce the figures and results and not the manuscript, you can just run "replication.r"---the R code extracted from replication.qmd. Running "replication.r" will not save the figures in the /figs/ folder as required to render the manuscript. 

# Data files (in /data/ folder)

The main replication data 

- "data/corr_counts.Rdata" - Counts of legislator contacts per year per agency (in the /data/ folder of this dataverse project)
   - see complete codebook and coding procedure in Supplemental Information Part B (SI.pdf)

Required data on members of Congress

- "data/member_data.rda" legislator covariates: (in the /data/ folder of this dataverse project)


# Dataset codebooks (in /docs/ folder)

## 1. Counts of legislator contacts per year per agency 

Codebook: "docs/corr_counts_codebook.pdf"

Data file: "data/corr_counts.Rdata"

Citation: Author-created data souce [@replication]

Variable names, descriptive labels, and values: 

- "icpsr"  = Legislator id                            
- "chamber"  = "House" or "Senate"                         
- "agency" = Agency acronym                            
- "year"  = Year  [2007:2020]                          
- "TYPE"  = Type of Legislator Request. See codebook in Suplimental Information.     
  - 1 ~ "Constituent (individual)"
  - 2 ~ "Constituent (corporate)"
  - 3 ~ "Constituent (501c3 or local\n government)"
  - 4 ~ "Policy (corporate)"
  - 5 ~ "Policy (general)"
- "per_icpsr_chamber_year_agency_type" = Count per legislator per year per agency per type [0:1440]


```{r}
load(here::here("data", "corr_counts.Rdata"))

dim(corr_counts)

head(corr_counts, 7)
```


## 2. Data on members of Congress

Codebook: "docs/member_data_codebook.pdf"

Data file:  "data/member_data.Rdata"

Citations: Author-created data souce  [@replication], including: 

   - year, chamber, and party from @dwnominate2018 via voteview.com (also available on dataverse)

   - committee positions from @StewartWoon2017 and @unitedstates

   - state population from @Census2019
   
Variable names, descriptive labels, and values: 

- "congress"     = Congress   [110-116]
- "chamber"      = "House" or "Senate"
- "bioname"      = name from voteview.com
- "first_year"    = First year serving in Congress  [1989:2020]
- "icpsr"        = ICPSR id number from voteview.com
- "district_code" = District number  [0:53]
- "state_abbrev" = State abbreviation
- "state"        = State name
- "pop2010"    = State population in 2010 [563,767:37,252,895] from @Census2019
- "committees"  = Committee assignments from @StewartWoon2017 and @unitedstates
- "chair"      = Committee chair [0 = no, 1 = yes] from @StewartWoon2017 and @unitedstates
- "ranking_minority" = Ranking minority [0 = no, 1 = yes]
- "majority"        = Majority party  [0 = no, 1 = yes]
- "presidents_party" = Same party as the president [0 = no, 1 = yes]
- "party"           = Political party ["(D)" = Democrat, "(R)" = Republican, "(I)" = Independent]

```{r}
load(here::here("data", "member_data.Rdata"))

dim(member_data)

head(member_data)
```

```{r, eval=FALSE}
member_data |> skimr::skim()
```



# Code files

- "replication.qmd" uses `corr_counts` and `member data` to reproduce all analyses in the paper and Supplemental Information (rendered [here](https://judgelord.github.io/corr/replication))
   - **NOTE:** this file produces intermediate data files saved to /data/, figures saved to /figs/, and model objects saved to /models/ directories, which are required to render the manuscript and SI. In addition to all figures in the paper, these intermediate files include: 
      - data/means.Rdata
      - models/models_total.Rdata
      - models/models_district.Rdata
      - models/models_ratio.Rdata
      - models/models_con.Rdata
      - models/models_policy.Rdata
      - models/models_district_con.Rdata
      - models/models_spillover_con.Rdata
      - models/models_spillover.Rdata
      - models/models_spillover_policy.Rdata
      - models/models_district_policy.Rdata
      - models/models_district_party.Rdata
   - "replication.r" is simply the R code extracted from  "replication.qmd" --- it will produce but not save figures
   
   

# Manuscript files 

- "corr.qmd" compiles the manuscript text, pulling in results from the intermediate files created by running replication.qmd 
   - "assets/congress2019.bib" is the required bib file
- "si.qmd" compiles the Supplemental Information text, pulling in saved results running replication.qmd

# Output files 

- "replication.pdf" is "replication.qmd" rendered to PDF 
- "replication.html" is "replication.qmd" rendered to HTML 
- "corr.pdf" is the manuscript text produced by "corr.qmd"
- "si.pdf" is the Supplemental Information text produced by "si.qmd" 


# Computing Environment: 

- Computer Processor: Apple M2 Max,	12 Cores 
- Computer Memory (RAM): 96 GB 

Software

- RStudio 2025.05.1+513

```{r}
sessionInfo()
```

Note: running replication.qmd or replication.r will install the required packages to render the manuscript, including `here`, `scales`, and `modelsummary`.

The following packages may be need to be installed to render qmd files (not required to simply reproduce the just the results using replication.r)

```
base64enc
digest
evaluate
glue
highr
htmltools
jsonlite
markdown
mime
rmarkdown
stringi
stringr
xfun
yaml
```

# References
