---
title: "README"
format: md
bibliography: "assets/congress2019.bib"
---

Replication code for "The Effects of Shifting Priorities and Capacity on Congressional Policy Work and Constituency Service: Evidence from a Census of Legislator Requests to U.S. Federal Agencies"

## Data files: 

###  The main replication data 

1. Counts of legislator contacts per year per agency: "data/corr_counts.Rdata" (on dataverse)

### Required data on members of Congress

2. legislator covariates: "data/member_data.rda" including: 

- year, chamber, and party retrieved from voteview.com (also available on dataverse)

- committee positions from @StewartWoon2017 and @unitedstates

- state population from the US Census


## Code files

- "docs/replication.qmd" uses `corr_counts` and `member data` to reproduce all analyses in the paper and Supplemental Information (rendered [here](https://judgelord.github.io/corr/replication))



## Data details 

```{r}
load(here::here("data", "corr_counts.Rdata"))

dim(corr_counts)

head(corr_counts, 7)
```

```{r, eval=FALSE, echo = FALSE}
library(tidyverse)
library(magrittr)
# checking data 
min(corr_counts$year)
max(corr_counts$year)
corr_counts %<>% filter(year > 2006) %>%
  left_join(member_data)

corr_counts |> skimr::skim()
```


- "icpsr"  = Legislator id                            
- "chamber"  = "House" or "Senate"                         
- "agency" = Agency acronym                            
- "year"  = Year                            
- "TYPE"  = Type of Legislator Request. See codebook in Suplimental Information.     
  - 1 ~ "Constituent (individual)"
  - 2 ~ "Constituent (corporate)"
  - 3 ~ "Constituent (501c3 or local\n government)"
  - 4 ~ "Policy (corporate)"
  - 5 ~ "Policy (general)"
- "per_icpsr_chamber_year_agency_type" = Count per legislator per year per agency per type

```{r}
load(here::here("data", "member_data.Rdata"))

dim(member_data)
```

- "congress"     = Congress   
- "chamber"      = "House" or "Senate"   
- "bioname"      = name from voteview.com   
- "first_year"    = First year serving in Congress  
- "icpsr"        = ICPSR id number from voteview.com    
- "district_code" = District number  
- "state_abbrev" = State abbreviation    
- "state"        = State name   
- "pop2010"    = State population in 2010      
- "committees"  = Committee assignments      
- "chair"      = Committee chair [0 = no, 1 = yes]   
- "ranking_minority" = Ranking minority [0 = no, 1 = yes] 
- "majority"        = Majority party  [0 = no, 1 = yes] 
- "presidents_party" = Same party as the president [0 = no, 1 = yes]
- "party"           = Political party


```{r}
head(member_data)
```