---
title: "Book Figures"
output:
    html_document:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
    #   toc: true
    #   keep_tex: true
    # pdf_document:
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
source("setup.R")

# override defaults 
knitr::opts_chunk$set(echo = TRUE, 
                      cache = TRUE, 
                      fig.width=8.5, 
                      fig.retina = 1)
```


# Data  
```{r, eval=TRUE}
FOIA <- read_csv(here("data/_FOIA_response_table.csv")) %>% select(-ends_with("1")) %>% 
  mutate(Department = Department %>% str_remove_all("Department of the|Department of ")) 

FOIA %>% 
  kablebox_long()

FOIA %>% select(-Coded) %>%
  rename(N = Observations) %>% 
  kable(format = "latex", booktabs = T) %>%
  row_spec(row = 16, hline_after = TRUE) %>%
  row_spec(row = 17, bold = T) %>% 
  #kable_styling(font_size = 9, full_width = TRUE) %>% 
       write_file(here::here("docs", "tables", "FOIA.tex")) 
```

```{r data, cache=FALSE}
# can't cache data

# new raw data 
load(
  here::here("data", "all_contacts.Rdata") %>% 
       str_replace("Correspondence","correspondence_data")
     ) 

all_contacts %>% count() %>% pull(n)  %>% write(file = here::here("docs/tables/n"))

all_contacts %>% count(TYPE != "NA") %>% pull(n) %>% .[[2]] %>% write(file = here::here("docs/tables/n_coded"))

n_agencies <- all_contacts $agency %>% unique() %>% length()

write(n_agencies, file = here::here("docs", "tables", "n_agencies"))
# 
# # old raw data 
# load(
#   here::here("data", "all_contacts2.Rdata") 
#      ) 

all_contacts |> count(agency) |> kablebox()

all_contacts |> count(year) |> kablebox()


# all_contacts %>% filter(year >2006, year <2018) %>%  dim()


all_contacts2 <- all_contacts #FIXME 

#load(here::here("data", "all_contacts_paper.Rdata"))

all_contacts2 %<>% mutate(type = ifelse(TYPE %in% c(1,2,3), "Constituency\nService", NA) ) %>%
  mutate(type = ifelse(TYPE %in% c(4,5), "Policy\nWork", type) )

all_contacts2$Type %<>% str_replace("Indiv. Constituent" , "Constituent (Individual)") %>% 
  str_replace("Corp. Constituent" , "Constituent (Corporate)")%>% 
  str_replace("501c3 or Local Gov." , "Constituent (501c3 or Local Gov.)")%>% 
  str_replace("Corp. Policy" , "Policy (Corporate)")%>% 
  str_replace("^Policy$" , "Policy (General)")


load(here::here("data", "dcounts_min.Rdata"))
load(here::here("data", "dcounts_tenure.Rdata"))
load(here::here("data", "dcounts_ratio.Rdata"))
load(here::here("data", "dcounts_per_district.Rdata"))


load(here::here("data", "members.Rdata"))

members %<>% mutate(member_state = member_state %>%
                     str_replace("\\) ", "-") %>%
                     str_c(")")) 


congress_years2<- function(congress){
		years<- c(congress*2 + 1787, congress*2 + 1788 ) %>% str_c(collapse = ";", sep = ";")
		return(years)
}

# FIXME members data should have years so we don't merge in observations for members in the january (final days of their last term)
# members2 <- members %>%
# mutate(year = congress %>%  congress_years2() %>% str_c(collapse = ";"))

# CAUTION THIS IS WRONG AND WILL PRINT OUT ALL YEARS IN DATA ^2
# members2$year[1]

load(here::here('data', 'agency_vars.Rdata'))

congress_years<- function(congress){
		years<- c(congress*2 + 1787, congress*2 + 1788 )
		return(years)
}

year_congress<- function(year){
	return(floor((year - 1787)/2))
}



d <- dcounts_min %>% 
  ungroup() %>% 
  mutate(type = ifelse(TYPE %in% c(1,2,3), "Constituency\nService", NA) ) %>%
  mutate(type = ifelse(TYPE %in% c(4,5), "Policy\nWork", type) )

type <- d %>% 
  group_by(type) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup()


# type %>% 
#   rename(type2 = type) %>%
#   mutate(percent = n/sum(type$n[1:2])*100) %>% 
#   kablebox()



type5 <- d %>% 
  group_by(TYPE) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() 

type5 %<>% 
  mutate(percent = n/sum(type5$n[2:6])*100 )

type5 %>% filter(TYPE !=" ") %>%  mutate(percent = round(percent)) %>% 
kablebox()


type2017 <- d %>% 
  filter(year> 2006, year < 2018) %>%
  group_by(type) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>%
  ungroup()

coded <- d %>% 
  mutate(coded = !is.na(type)) %>% 
  group_by(coded) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) 

coded_ratio = coded$n[2]/(sum(coded$n))

multiplier = sum(coded$n)/coded$n[2]

percent <- function(x){
  y <- x*100 
  y %<>% round() 
  return(y)}
# percent(.434534523453)

d %<>% filter(chamber != "President")

d %<>% mutate(congress = year_congress(year))




dcounts <- d %>% left_join(members)


type2xchair <- dcounts %>% 
  group_by(type, chair) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  drop_na(type, chair) %>% 
  group_by(chair) %>% 
  mutate(percent = n / sum(n) *100) 


type2xprestigechair <- dcounts %>% 
  group_by(type, prestige_chair) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  drop_na() %>% 
  group_by(prestige_chair) %>% 
  mutate(percent = n / sum(n) *100) 

# prestige committee
type2xprestige <- dcounts %>% 
  group_by(type, prestige) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  drop_na() %>% 
  group_by(prestige) %>% 
  mutate(percent = n / sum(n) *100) 


type2xchamber <- dcounts %>%
  group_by(type, chamber) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  drop_na() %>% 
  group_by(chamber) %>% 
  mutate(percent = n / sum(n) *100) 


# year
type2xyear <- dcounts %>% mutate(years = year  - yearelected) %>% 
  group_by(type, years) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  drop_na() %>% 
  group_by(years) %>% 
  mutate(percent = n / sum(n) *100) 
```

## Counts

```{r counts-by-type}
n <- dcounts |> ungroup() |>  group_by(chamber, member_state, icpsr, TYPE) |> summarise(n = sum(per_icpsr_chamber_year_agency_type))  
  
n1 <- filter(n, TYPE == 1) |> distinct(member_state, icpsr, chamber, n1 = n) 
n2 <- filter(n, TYPE == 2) |> distinct(member_state, icpsr, chamber, n2 = n)
n3 <- filter(n, TYPE == 3) |> distinct(member_state, icpsr, chamber, n3 = n)
n4 <- filter(n, TYPE == 4) |> distinct(member_state, icpsr, chamber, n4 = n)
n5 <- filter(n, TYPE == 5) |> distinct(member_state, icpsr, chamber, n5 = n)

n <- dcounts |> ungroup() |>  group_by(chamber, member_state, icpsr) |> summarise(n = sum(per_icpsr_chamber_year_agency_type))  

ns <- list(n$n, n1$n1, n2$n2, n3$n3, n4$n4, n5$n5)


ttest <- function(x, y){
  pvalue <- t.test(x, y) %>% .$p.value
  stat <-  t.test(x, y) %>% .$`statistic`
  
  return(paste("t =", round(stat, 1), "    p =", round(pvalue, 2)))
}

t <- tibble(
  . = c("Overall", "Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
  Overall = map2_chr(list(n$n), ns, ttest),
  Type1 = map2_chr(list(n1$n1), ns, ttest),
  Type2 = map2_chr(list(n2$n2), ns, ttest),
  Type3 = map2_chr(list(n3$n3), ns, ttest),
  Type4 = map2_chr(list(n4$n4), ns, ttest),
    Type5 = map2_chr(list(n5$n5), ns, ttest)
)

t %>% kablebox_long()


chitest <- function(x, y){
  pvalue <- chisq.test(x, y) %>% .$p.value
  stat <-  chisq.test(x, y) %>% .$`statistic`
  
  return(paste("Chi-sq =", round(stat, 1), " p =", pvalue))
}

chi <- tibble(
  . = c("Overall", "Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
  Overall = map2_chr(list(n$n), ns, chitest),
  Type1 = map2_chr(list(n1$n1), ns, chitest),
  Type2 = map2_chr(list(n2$n2), ns, chitest),
  Type3 = map2_chr(list(n3$n3), ns, chitest),
  Type4 = map2_chr(list(n4$n4), ns, chitest),
    Type5 = map2_chr(list(n5$n5), ns, chitest)
)

chi %>% kablebox_long()

```



Between February 2017 and February 2021, we received data on `r as.integer(sum(type$n))` instances of members of Congress contacting federal agencies. We focus on requests made from 2007-2017, resulting in a data set of `r as.integer(sum(type2017$n))` contacts from members of Congress with federal agencies.


## Requests by percentile


```{r percentiles-by-type, fig.height=13.4, fig.width=6, cache=TRUE}
# add percentile by type 


p <- dcounts %>% 
  filter(TYPE %in% c(1,2,3,4,5)) %>% 
    group_by(member_state, chamber, year, TYPE) %>% summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>%
  group_by(member_state, chamber, TYPE) %>% 
  summarise(mean = mean(n)) %>% 
  ungroup() %>% 
    group_by(chamber, TYPE) %>% 
  mutate(Percentile = ntile(mean, 100),
         rank = dense_rank(-mean)) %>% 
  arrange(-Percentile) %>% 
  dplyr::select(member_state, Percentile, mean, chamber,rank) %>% distinct() 

p %>% 
    ggplot() + 
    geom_col(aes(x = Percentile, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile, y = mean, label = ifelse(rank <14 | Percentile < 30, member_state, "")), check_overlap = T, 
                  size = 2,
                  hjust = "inward") + 
  theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile Within Chamber",
       y = "Average Requests per Year") +     facet_grid(TYPE ~ chamber , scales = "free_y") 

  
```



## Percentile by type

### Chi-sq test 
```{r}
p <- dcounts %>% 
  filter(TYPE %in% c(1,2,3,4,5)) %>% 
    group_by(member_state, chamber, year, TYPE) %>% summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>%
  group_by(member_state, chamber, TYPE) %>% 
  summarise(mean = mean(n)) %>% 
  ungroup() %>% 
    group_by(chamber, TYPE) %>% 
  mutate(Percentile = ntile(mean, 100),
         rank = dense_rank(-mean)) %>% 
  arrange(-Percentile) %>% 
  dplyr::select(member_state, Percentile, mean, chamber,rank) %>% distinct() %>% 
  ungroup()


p1 <- filter(p, TYPE == 1) |> distinct(member_state, chamber, Percentile1 = Percentile) |> arrange(member_state)
p2 <- filter(p, TYPE == 2) |> distinct(member_state, chamber, Percentile2 = Percentile)|> arrange(member_state)
p3 <- filter(p, TYPE == 3) |> distinct(member_state, chamber, Percentile3 = Percentile)|> arrange(member_state)
p4 <- filter(p, TYPE == 4) |> distinct(member_state, chamber, Percentile4 = Percentile)|> arrange(member_state)
p5 <- filter(p, TYPE == 5) |> distinct(member_state, chamber, Percentile5 = Percentile)|> arrange(member_state)

p %<>% left_join(p1) %>% left_join(p2) %>% left_join(p3) %>% left_join(p4) %>% left_join(p5)

percentiles <- list(#p$Percentile,# PLACIBO: runif(n = length(p$Percentile)), 
                    p1$Percentile1, p2$Percentile2, p3$Percentile3, p4$Percentile4, p5$Percentile5)

ttest <- function(x, y){
  pvalue <- t.test(x, y) %>% .$p.value
  stat <-  t.test(x, y) %>% .$`statistic`
  
  return(paste("t =", round(stat, 1), "    p =", pvalue))
}

t <- tibble(
  . = c(#"Overall", 
        "Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
  #Overall = map2_chr(list(p$Percentile), percentiles, ttest),
  Type1 = map2_chr(list(p1$Percentile1), percentiles, ttest),
  Type2 = map2_chr(list(p2$Percentile2), percentiles, ttest),
  Type3 = map2_chr(list(p3$Percentile3), percentiles, ttest),
  Type4 = map2_chr(list(p4$Percentile4), percentiles, ttest),
    Type5 = map2_chr(list(p5$Percentile5), percentiles, ttest)
)

t %>% kablebox_long()


chitest <- function(x, y){
  pvalue <- chisq.test(x, y) %>% .$p.value
  stat <-  chisq.test(x, y) %>% .$`statistic`
  
  return(paste("Chi-sq =", round(stat, 1), " p =", round(pvalue, 3)))
}

chi <- tibble(
  . = c(#"Overall", 
    "Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
  #Overall = map2_chr(list(p$Percentile), percentiles, chitest),
  Type1 = map2_chr(list(p1$Percentile1), percentiles, chitest),
  Type2 = map2_chr(list(p2$Percentile2), percentiles, chitest),
  Type3 = map2_chr(list(p3$Percentile3), percentiles, chitest),
  Type4 = map2_chr(list(p4$Percentile4), percentiles, chitest),
    Type5 = map2_chr(list(p5$Percentile5), percentiles, chitest)
)

chi %>% kablebox_long()
```


```{r eval=FALSE}
chitest <- function(x, y){
  stat <-  chisq.test(x, y) %>% .$`statistic`
  
  return(stat |> round(-3)/1000)
}

chi <- tibble(
  x = c(#"Overall", 
    "Type 1", "Type 2", "Type 3", "Type 4", "Type 5"),
  #Overall = map2_dbl(list(p$Percentile), percentiles, chitest),
  Type1 = map2_dbl(list(p1$Percentile1), percentiles, chitest),
  Type2 = map2_dbl(list(p2$Percentile2), percentiles, chitest),
  Type3 = map2_dbl(list(p3$Percentile3), percentiles, chitest),
  Type4 = map2_dbl(list(p4$Percentile4), percentiles, chitest),
    Type5 = map2_dbl(list(p5$Percentile5), percentiles, chitest)
)

chi %>% 
  kable(caption = "Chi-sq / 1k")
  # kableExtra::column_spec("Overall", color = chi$Overall)
  # pivot_longer(everything()) %>% 
  # filter(name != "x")
  # ggplot() + 
  # aes(?)


```

### By Type 1

```{r percentiles-by-type1, fig.height=13.4, fig.width=6, cache=TRUE}

p %>% 
    ggplot() + 
    geom_col(aes(x = Percentile1, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile1, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile1, 
                y = mean, 
                label = ifelse(rank <30 | Percentile < 30, member_state, "")), 
            check_overlap = T, 
            size = 2,
            hjust = "inward") + 
  theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile Type 1 Within Chamber",
       y = "Average Requests per Year") +     
  facet_grid(TYPE ~ chamber , scales = "free_y") 
```

### By Type 2
```{r percentiles-by-type2, fig.height=13.4, fig.width=6, cache=TRUE}
# add percentile by type 

p %>% 
    ggplot() + 
    geom_col(aes(x = Percentile2, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile2, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile2, 
                y = mean, 
                label = ifelse(rank <30 | Percentile < 30, member_state, "")), 
            check_overlap = T, 
            size = 2,
            hjust = "inward") + 
  theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile Type 2 Within Chamber",
       y = "Average Requests per Year") +     
  facet_grid(TYPE ~ chamber , scales = "free_y") 
```

### By Type 3
```{r percentiles-by-type3, fig.height=13.4, fig.width=6, cache=TRUE}
# add percentile by type 

p %>% 
    ggplot() + 
    geom_col(aes(x = Percentile3, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile3, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile3, 
                y = mean, 
                label = ifelse(rank <30 | Percentile < 30, member_state, "")), 
            check_overlap = T, 
            size = 2,
            hjust = "inward") + 
  theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile Type 3 Within Chamber",
       y = "Average Requests per Year") +     
  facet_grid(TYPE ~ chamber , scales = "free_y") 
```

### By Type 4
```{r percentiles-by-type4, fig.height=13.4, fig.width=6, cache=TRUE}
# add percentile by type 

p %>% 
    ggplot() + 
    geom_col(aes(x = Percentile4, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile4, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile4, 
                y = mean, 
                label = ifelse(rank <30 | Percentile < 30, member_state, "")), 
            check_overlap = T, 
            size = 2,
            hjust = "inward") + 
  theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile Type 4 Within Chamber",
       y = "Average Requests per Year") +     
  facet_grid(TYPE ~ chamber , scales = "free_y") 
```

### By Type 5
```{r percentiles-by-type5, fig.height=13.4, fig.width=6, cache=TRUE}
# add percentile by type 

p %>% 
    ggplot() + 
    geom_col(aes(x = Percentile5, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile5, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile5, 
                y = mean, 
                label = ifelse(rank <30 | Percentile < 30, member_state, "")), 
            check_overlap = T, 
            size = 2,
            hjust = "inward") + 
  theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile Type 5 Within Chamber",
       y = "Average Requests per Year") +     
  facet_grid(TYPE ~ chamber , scales = "free_y") 
```
