---
title: "Replication Code and Robustness Checks"
subtitle: "The Effects of Shifting Priorities and Capacity on Elected Officials' Policy Work and Constituency Service: Evidence from a Census of Legislator Requests to U.S. Federal Agencies"
format:
    html: 
      toc: true
      code-fold: true
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
library(modelsummary)
library(marginaleffects)
library(fixest)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(here)
library(ggrepel)

knitr::opts_chunk$set(echo = T, # code is folded 
                      cache = F, # CACHE 
                      fig.width = 4.5, 
                      fig.height = 3.5,
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      fig.retina = 6,
                      warning = F, 
                      message = F)

# inline numbers round to 2, comma at thousands
inline <- function(x) {
  if (is.na(as.numeric(x))) {
    return (x)
    } else
        return (as.numeric(x) |> 
                 round(2) |>
                 format(big.mark=",") 
        )
}

knitr::knit_hooks$set(inline = inline)

# plot defaults 
library(ggplot2); theme_set(
      theme_minimal() + 
        theme(
          # FOR AJPS
          panel.grid = element_blank(),
          legend.position = "bottom",
          # END FOR AJPS 
          panel.border  = element_blank(),
          panel.grid.major.x = element_blank())
                            )
  options(
    ggplot2.continuous.color = "cividis",
    ggplot2.continuous.fill = "cividis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(..., direction = -1)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(..., direction = -1)
  
# html table formatting
kablebox <- . %>%  
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "200px")

kablebox_long <- . %>% 
  head(100) %>% 
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px")
```


# Theory 

```{r 2x2-fig, fig.show="hold", echo=FALSE}
#| label: 2x2-fig
#| fig-width: 3.6
#| fig-height: 3.6
#| layout-ncol: 2


# CAPACITY
capacity <- tibble::tibble(
  priority = .2,
  capacity = c(100, NA, NA, NA, NA, 150)
  ) %>% 
  ggplot() +
  aes(x = capacity*priority,
      y = capacity*(1-priority) ,
      label = str_c(capacity*priority, ", ", capacity*(1-priority))) + 
   geom_segment(x = c(0,0,0,0,0,0),
                 xend = c(100, 110, 120,130,140, 150),
                 y = c(100, 110, 120,130,140, 150),
                 yend = c(0,0,0,0,0,0),
              linetype = 1,
              alpha = c(.1,.2,.4,.6,.8,1)) + 
    geom_point(alpha = c(.5, 1,1,1,1,1) ) +
  geom_segment(x = 100*.2, 
           y = 100*.8,
           xend = 148*.2, 
           yend = 148*.8,
           arrow = arrow(type = "closed", length = unit(.1, "in")),
           color = "blue") + 
  annotate("text", 
          label = "50% increase in capacity while maintaining\na 80:20 ratio of constituency service to\npolicy work (80% constituency service)", 
           x = 150*.2, 
           y = 150*.8,
          hjust = -.01,
          vjust = -.1,
          color = "black",
          size = 3) +
  geom_label(x = 0, 
             y = c(100, 110, 120,130,140, 150), 
             label = c("1x", NA, NA, NA, NA, "1.5x"),
             size = 3,
             hjust = .44 ) + 
    scale_y_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  scale_x_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  labs(title = "",
       x = "Volume of policy work",
       y = "Volume of constituency service") + 
  theme(legend.position = "", 
        panel.grid.minor = element_blank() )




# PRIORITY 
priority <- tibble::tibble(
  priority = c(.2, .4),
  capacity = c(100) 
  ) %>% 
  mutate(
    x = capacity*priority,
      y = capacity*(1-priority)
  ) %>% 
  ggplot() +
  aes(x = x,
      y = y ) + 
        geom_segment(x = c(0),
                 xend = c(100),
                 y = c(100),
                 yend = c(0),
              linetype = 1,
              alpha = c(.1)) +
   stat_function(fun =  ~ 4*.x , geom = "line", linetype = 2, alpha = .1) +
     stat_function(fun =  ~ 3.5*.x , geom = "line", linetype = 2, alpha = .2) +
   stat_function(fun =  ~ 3*.x , geom = "line", linetype = 2, alpha = .4) +
   stat_function(fun =  ~ 2.5*.x , geom = "line", linetype = 2, alpha = .6) +
   stat_function(fun =  ~ 2*.x , geom = "line", linetype = 2, alpha = .8) +
   stat_function(fun =  ~ 1.5*.x , geom = "line", linetype = 2, alpha = 1) +
  geom_point(alpha = c(.5,1) ) +
  geom_segment(x = 100*.2, 
           y = 100*.8,
           xend = 100*.4, 
           yend = 100*.6,
           arrow = arrow(type = "closed", length = unit(.1, "in")),
           color = "blue") + 
  annotate("text", 
          label = "Shifting priority toward policy work\nwithout increasing capacity", 
           x = 100*.4, 
           y = 100*.6,
          hjust = -.01,
          vjust = 1.1,
          color = "black",
          size = 3) +
  geom_label(aes(x = 150*c(.24, .66),
                 y = 150 ),
             label = c("80:20", "60:40"),
          size = 3) + 
  scale_y_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  scale_x_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  #scale_color_gradient(low = "grey", high = "black") +
  labs(title = "",
       x = "Volume of policy work",
       y = "Volume of constituency service") +
  theme(legend.position = "",         
        #panel.grid.major = element_blank(),
        panel.grid.minor = element_blank() )



# BOTH  
both <- tibble::tibble(
  priority = c(.2, .4),
  capacity = c(100, 150) 
  ) %>% 
  mutate(
    x = capacity*priority,
      y = capacity*(1-priority)
  ) %>% 
  ggplot() +
  aes(x = x,
      y = y ) + 
      geom_segment(x = c(0, 0),
                 xend = c(100,150),
                 y = c(100, 150),
                 yend = c(0,0),
              linetype = 1,
              alpha = c(.1, 1)) +
   stat_function(fun =  ~ 4*.x , geom = "line", linetype = 2, alpha = .1) +
   stat_function(fun =  ~ 1.5*.x , geom = "line", linetype = 2, alpha = 1) +
  geom_label(aes(x = 150*c(.24, .66),
                 y = 150 ),
             label = c("80:20", "60:40"),
          size = 3) + 
    geom_point(alpha = c(.5,1) ) +
  geom_segment(x = 100*.2, 
           y = 100*.8,
           xend = 148*.4, 
           yend = 149*.6,
           arrow = arrow(type = "closed", length = unit(.1, "in")),
           color = "blue") + 
  annotate("text", 
          label = "Shifting priority toward policy work\n AND increasing capacity by 50%", 
           x = 150*.4, 
           y = 150*.6,
          hjust = .06,
          vjust = -.5,
          color = "black",
          size = 3) +
    geom_label(x = 0, y = c(100, 150), 
             label = c("1x", "1.5x"),
             size = 3,hjust = .44) + 
  scale_y_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  scale_x_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  #scale_color_gradient(low = "grey", high = "black") +
  labs(title = "",
       x = "Volume of policy work",
       y = "Volume of constituency service") + 
  theme(legend.position = "",          panel.grid.minor = element_blank() )



# Regions   
more_c <- tibble(x = c(0, 20, 37.5,0),
       y = c(100, 80, 150,150) ) %>% 
  mutate(label = "A")

less_c <- tibble(x = c(0, 20, 0,0),
       y = c(0, 80, 80, 0) ) %>% 
  mutate(label = "D")


more_p <- tibble(x = c(19.8, 37.5, 150, 150),
       y = c(79, 150, 150, 79) ) %>% 
  mutate(label = "B")

less_p <- tibble(x = c(100, 21, 150, 150),
       y = c(0, 79, 79, 0) ) %>% 
  mutate(label = "C")


# REGIONS 
regions <- more_p %>%
 full_join( less_p) %>% #full_join(more_c) %>% 
  group_by(label) %>% 
  mutate(mean_x = mean(x),
         mean_y = mean(y),
         name = label %>% 
           str_replace("B", #"c_{i1}p_{i1} > c_{i2}p_{i2}" #FIXME 
                       "The effect of increasing capacity is large\nenough that levels of constituency service\nare maintained or increase, even as\nelected officials prioritize policy work."
                       ) %>% 
           str_replace("C", "Shifting priorities toward policy\ncauses less constituency service"
           #expression("$c_{i1}p_{i1} > c_{i2}p_{i2}$" #FIXME 
           )
         ) %>% 
  ungroup() %>% 
ggplot() +
  aes(x = x,
      y = y,
      fill = label,
      label = name) + 
  geom_polygon( alpha = .5) + 
    geom_segment(x = 0,
                 xend = 100,
                 y = 100,
                 yend = 0,
              linetype = 1,
              alpha = c(.01)) +
     stat_function(fun =  ~ 4*.x , geom = "line", linetype = 2, alpha = .1) +
  geom_point(x = 20, y = 80, alpha = .5, color = "grey") + 
  scale_fill_grey() +
  scale_y_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  scale_x_continuous(breaks = seq(0, 140, by = 20), limits = c(0, 150)) + 
  geom_text(aes(x = mean_x, y = mean_y), 
            check_overlap = T, 
            #parse = T,
          size = 3,
          vjust =.5) + 
  labs(title = "",
       x = "Volume of policy work",
       y = "Volume of constituency service") + 
  theme(legend.position = "",          panel.grid.minor = element_blank() )


capacity  
priority 
both  
regions


```


# Replication data

```{r data}
load(here::here("data", "corr_counts.Rdata"))
load(here::here("data", "members.Rdata"))

corr_counts  %<>% filter(year > 2006, year < 2021)


members

members %<>% mutate(member_state = member_state %>%
                     str_replace("\\) ", "-") %>%
                     str_c(")")) 

d <- corr_counts %>% 
  ungroup() %>% 
  mutate(Type = case_when(
    TYPE %in% c(1,2,3) ~ "Constituency\nService", 
    TYPE %in% c(4,5) ~ "Policy"), 
         type = case_when(
            TYPE == 1 ~ "Constituent (individual)",
            TYPE == 2 ~ "Constituent (corporate)",
            TYPE == 3 ~ "Constituent (501c3 or local\n government)",
            TYPE == 4 ~ "Policy (corporate)",
            TYPE == 5 ~ "Policy (general)"
         )) 

type <- d %>% 
  group_by(Type) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup()

type2017 <- d %>% 
  filter(year> 2006, year < 2018) %>%
  group_by(type) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>%
  ungroup()

percent <- function(x){
  y <- x*100 
  y %<>% round() 
  return(y)}

year_congress<- function(year){
  return(floor((year - 1787)/2))
}

d %<>% mutate(congress = year_congress(year))



dcounts <- d |> left_join(members)
```



##  Example

Rep. Barbara Comstock worked in Rep. Frank Wolf's congressional office for five years, described him as a "longtime mentor," and claimed that Wolf first urged her to run for office. He endorsed and campaigned with her. 

Notice several patterns
- dip in constituency service when Wolf is no longer running for re-election
- further dip with transition
- quick rebound as Comstock gets her office in order
- inheriting a highly-effective office, Comstock is far above average house member


```{r cases, eval=FALSE}
members %<>% mutate(cqlabel = paste0("(", state_abbrev, "-", district_code, ")") |> str_remove("-0"))

case_study <- function(cq){

  CHAMBER <- filter(members, cqlabel == cq) %>% 
    .$chamber %>% .[1]

dcounts %>% 
  group_by(member_state, year, chamber, cqlabel) %>% summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  group_by(chamber) %>% 
  mutate(mean_per_chamber = mean(n) %>% round(0)) %>% 
  filter(cqlabel == cq, year > 2007, year <2017) %>% 
  ggplot() +
  aes(x = year, 
      y = n, 
      fill = member_state %>% str_replace("-.*", "\\)")) + 
  geom_col(alpha = .5, position = "dodge") +
  geom_hline(aes(yintercept = mean_per_chamber), linetype = 2) + 
  geom_text(aes(y = mean_per_chamber), 
            x = 2007.5, 
            label = "Chamber average", check_overlap = T,
            size = 3, vjust = 1.3, hjust = 0) + 
  scale_x_continuous(breaks = seq(2008, 2016, 1)) +
  labs(x = "",
       y = "Number of requests", 
       fill = str_c(CHAMBER, "-", cq) %>% str_remove_all("\\(|\\)") ) + 
  # theme_minimal() + 
  theme(panel.grid.major.x =  element_blank(),         legend.position = "bottom",
        panel.grid.minor.x =  element_blank(),
        axis.text.x = element_text(angle = 45))+ 
    scale_fill_viridis_d(begin = 0, end = .6, option = "cividis", direction = -1) 
  
ggsave(str_c("figs/districts/", cq, ".png"), 
       width = 5.7,
  height = 2.5,
  dpi = 1000)
} 

case_study("(WI)")

case_study("(WI-07)")

case_study("(VA-10)")

case_study("(NY-07)")

case_study("(NY-14)")



cases <- unique(members$cqlabel) #%>% head()

# map(cases, case_study )

```

---

Between February 2017 and February 2021, we received data on `r as.integer(sum(type$n))` instances of members of Congress contacting federal agencies. We focus on requests made from 2007-2012, resulting in a data set of `r as.integer(sum(type2017$n))` contacts from members of Congress with federal agencies.


## Requests by percentile


```{r percentiles, fig.height=3.4, fig.width=6, cache=TRUE}

percentiles <- dcounts %>% 
  filter(year > 2006, year < 2021) %>% 
    group_by(member_state, chamber, year) %>% summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>%
  group_by(member_state, chamber) %>% 
  summarise(mean = mean(n)) %>% 
  ungroup() %>% 
    group_by(chamber) %>% 
  mutate(Percentile = ntile(mean, 100),
         rank = dense_rank(-mean)) %>% 
  arrange(-Percentile) %>% 
  dplyr::select(member_state, Percentile, mean, chamber,rank) %>% distinct() 


percentiles |> arrange(rank) |> kablebox()

percentiles |> group_by(chamber) |> summarise(chamber_average = mean(mean)) |> kablebox()

percentiles %>% 
    ggplot() + 
    geom_col(aes(x = Percentile, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile, y = mean, 
                label = ifelse(rank <24 | Percentile < 50,
                               member_state, "")), 
            check_overlap = T, 
                  size = 3,
                  hjust = "inward") + 
  # theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile within chamber",
       y = "Average requests per year") +     facet_grid(. ~ chamber , scales = "free_y") 

  
```


## Requests by year

```{r counts-per-year, fig.height=3, fig.width=5.7, cache=TRUE, eval=TRUE}
dcounts %<>% 
  group_by(bioname, year) %>% 
  mutate(per_bioname_year = sum(per_icpsr_chamber_year_agency_type)) %>%
  ungroup() %>% 
  group_by(year) %>%
  #mutate(per_bioname_year = per_bioname_year - mean(per_bioname_year)) %>% 
  ungroup() 

schumer2013 <- dcounts %>% filter(bioname == "SCHUMER, Charles Ellis (Chuck)",
                   year == 2013) %>% .$per_bioname_year %>% unique()

cruz2013 <- dcounts %>% filter(bioname == "CRUZ, Rafael Edward (Ted)",
                   year == 2013) %>% .$per_bioname_year %>% unique()

mcconnell2013 <- dcounts %>% filter(bioname == "McCONNELL, Addison Mitchell (Mitch)",
                   year == 2013) %>% .$per_bioname_year %>% unique()


p <- dcounts %>% 
  filter(year > 2006, year <2018) %>%
  distinct(bioname, per_bioname_year, year, chamber) %>% 
  filter(per_bioname_year > 0) %>% 
  ggplot() + 
  geom_line(aes(x = year, 
                y = per_bioname_year, 
                group = bioname, 
                color = chamber), 
            alpha = .1) +
  geom_line(aes(x = year, 
                group = bioname, 
                color = chamber,
                y = ifelse(bioname == "SCHUMER, Charles Ellis (Chuck)", per_bioname_year, NA))) + 
  geom_label(x = 2013, 
             y = schumer2013, 
             label = "Chuck Schumer") +
  geom_line(aes(x = year, group = bioname, color = chamber,
                y = ifelse(bioname == "CRUZ, Rafael Edward (Ted)", per_bioname_year, NA))) + 
  geom_label(x = 2013, 
             y = cruz2013, 
             label = "Ted Cruz") +
  geom_line(aes(x = year, group = bioname, color = chamber,
                y = ifelse(bioname == "McCONNELL, Addison Mitchell (Mitch)", per_bioname_year, NA))) + 
  geom_label(x = 2013, 
             y = mcconnell2013, 
             label = "Mitch McConnell") +
  labs(x = "",
       color = " ",
       y = paste("Requests per legislator per year"),
       title = "") +
  scale_x_continuous(breaks = unique(dcounts$year)) + 
  scale_color_viridis_d(begin = 0, end = .6, option = "cividis", direction = -1) 

# FIXME, this takes a long time 
p +
  # theme_minimal() + 
  theme(panel.background = element_blank(), 
        # AJPS formatting 
        legend.position = "inside",
        legend.position.inside = c(1, 1),
        #FIXME 
        legend.justification.inside = c(1, 1), 
        axis.ticks = element_blank(),
        axis.text.x = element_text(angle = 30, vjust = 0)) 
```   

## Requests by state population

```{r pop, fig.width=6, fig.height=4}
dcounts %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
    group_by(member_state, pop2010) %>%
  summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = pop2010, y = mean), color = "light blue") + 
    geom_smooth(aes(x = pop2010, y = mean)) + 
  geom_text_repel(aes(x = pop2010, 
                y = mean, 
                label = ifelse(mean > 390 | log(pop2010) > 17.0 | 
                                 mean < 100,# & (log(pop2010) > 27 | log(pop2010) < 14), 
                               member_state, 
                               "")), 
            seed = 44,
            check_overlap = T, 
            min.segment.length = 0,
            size = 3) + theme_bw() +
  labs(title = "",
       x = "State population (log scale)",
       y = "Average number of requests per year") +
  scale_x_log10(labels = scales::comma) +
  theme_minimal() + 
  theme(panel.grid = element_blank())
```   

---



## Types of requests


`r percent(type$n[1]/(type$n[1]+type$n[2]) )`% of the average legislators' contacts with agencies are about constituency service.

`r percent(type$n[2]/(type$n[1]+type$n[2]))`% of the average legislators' contacts with agencies are about policy work.

```{r} 
type %>% kablebox()
```

We classify legislator requests into five overall types:

All data:
```{r data_by_type-tall, fig.height=3.5, fig.width=5.5}
# paper figure 
type_totals <- d %>% 
  drop_na(Type) %>%  
  mutate(total = sum(per_icpsr_chamber_year_agency_type)) %>% 
  group_by(total, Type, type) %>% 
  summarise(nT =  sum(per_icpsr_chamber_year_agency_type)) %>% 
  mutate(percent = paste0(nT, " = ", 100*round(nT/total, 2), "%"),
         type = str_c(type, "\n    ", percent)) %>% 
  ungroup() %>% 
  group_by(Type) %>% 
  mutate(nt = sum(nT),
         percent_t = paste0(100*round(nt/total, 2), "%"))

type_totals %<>% mutate(type = type %>% 
                          str_replace_all("\\)", "") %>% 
                          str_replace_all(" \\(", ",\n") )

N <- type_totals$total |> unique()


# horizontal
type_totals %>% 
  ungroup() %>% 
  ggplot() + 
  geom_col(alpha = .7,aes(x = type, fill = Type, y = nT) ) + 
  scale_y_continuous(breaks = seq(0,500000, 50000), limits = c(0,500000)) + 
  labs(x = "",
       fill = "",
       y = paste("Number of contacts"),
       title = "") +
  #geom_text(aes(label = Type, x = Type,y = nT) ) + 
  theme(panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank(),
        #axis.text.x.top = element_text(),
        legend.position ="none") + 
  ggpubr::geom_bracket(
    xmin = type_totals$type[1], xmax = type_totals$type[3], 
    y.position = 380000,
    label = paste(type_totals$percent_t[1], "Constituency service" ),
    #hjust = 1,
    vjust = -1
  ) + 
  ggpubr::geom_bracket(
    xmin = type_totals$type[4], xmax = type_totals$type[5], 
    y.position = 85000,
    label = paste(type_totals$percent_t[5], "Policy work"),
    #hjust = 1,
    vjust = -1
  )+ 
  scale_fill_viridis_d(option = "cividis", end = .8, direction = -1)
```