---
title: "member_data.Rdata codebook"
format: pdf
author: Devin Judge-Lord, Eleanor Neff Powell, Justin Grimmer
bibliography: "assets/congress2019.bib"
---

# Data on members of Congress

Title/file name: member_data.Rdata 

Citations: Author-created data souce  [@replication], including: 

   - year, chamber, and party from @dwnominate2018 via voteview.com (also available on dataverse)

   - committee positions from @StewartWoon2017 and @unitedstates

   - state population from @Census2019

Variable names, descriptive labels, and values: 

- "congress"     = Congress   [110-116]
- "chamber"      = "House" or "Senate"
- "bioname"      = name from voteview.com
- "first_year"    = First year serving in Congress  [1989:2020]
- "icpsr"        = ICPSR id number from voteview.com
- "district_code" = District number  [0:53]
- "state_abbrev" = State abbreviation
- "state"        = State name
- "pop2010"    = State population in 2010 [563,767:37,252,895]
- "committees"  = Committee assignments
- "chair"      = Committee chair [0 = no, 1 = yes]
- "ranking_minority" = Ranking minority [0 = no, 1 = yes]
- "majority"        = Majority party  [0 = no, 1 = yes]
- "presidents_party" = Same party as the president [0 = no, 1 = yes]
- "party"           = Political party ["(D)" = Democrat, "(R)" = Republican, "(I)" = Independent]

```{r}
load(here::here("data", "member_data.Rdata"))

dim(member_data)

head(member_data)
```

```{r, eval=TRUE}
member_data |> skimr::skim()
```

# Refrences
