---
title: "Reproduceable Example Code"
output:
    html_document:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
    # pdf_document:
    #   toc: true
    #   keep_tex: true
    #   header-includes:
    #    - \usepackage{subfig}
# editor_options: 
#   chunk_output_type: console
---


```{r global.options, include=FALSE}
library(modelsummary)
library(marginaleffects)
library(fixest)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(here)
library(ggrepel)

knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=4.5, 
                      fig.height = 3.5,
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      fig.retina = 6,
                      warning=FALSE, 
                      message=FALSE)

# inline numbers round to 2
knit_hooks$set(inline = function(x) {
  if (is.na(as.numeric(x))) {
    return(x)
    } else 
        return(round(x,2))
})


# plot color defaults 
library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "cividis",
    ggplot2.continuous.fill = "cividis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(..., direction = -1)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(..., direction = -1)
  
# html table formatting
kablebox <- . %>%  
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "200px")

kablebox_long <- . %>% 
  head(100) %>% 
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px")
```

Based on the [replication code](https://judgelord.github.io/corr/replication) for [this paper](https://judgelord.github.io/corr/corr.pdf), this workbook aims to explore Reviewer 2s objection: 

> "All legislators that remain in the dataset between t and t+1 increase in experience 1 unit. Thus, there is no identifying variation to separate the effect of experience from the effect of time shocks in the within-individual specification.

> Thus, the coefficients on the dummy variables indicating different levels of legislative experience are not identified in the OLS regression with time- and legislator fixed effects." 



# Replication data

From `code/replication.R`, which starts with the main data file (`dcounts_min.Rdata`) and makes transformations for three sets of models: 

1. counts per member-year (dcounts_tenure.Rdata/AgencyComm.dta)
2. ratio per member-year (dcounts_ratio.Rdata/ProportionContact.dta)
3. counts per district-year (dcounts_per_district.Rdata, DistrictLevel.dta)

The same three datasets are used in Replication.do

```{r data}
load(here::here("data", "dcounts_tenure.Rdata"))
load(here::here("data", "dcounts_ratio.Rdata"))
load(here::here("data", "dcounts_per_district.Rdata"))
load(here::here("data" , "members.Rdata"))


# var names for tables
dcounts_tenure %<>% 
  mutate(Legislator = icpsr,
         Legislator_x_Agency = icpsr_agency,
         Year_x_Agency = agency_year)

dcounts_tenure %>% head() %>% kablebox()
```

Reviewer 2s objection is about the models using (1) counts per member-year, so that is the DV I focus on here. 

### Values to predict at

The most frequent legislator agency pair: McCain x VA with 2159 letters.

The average is 73 letters per legislator per year, a little over 1.29 letters per agency per year.

For predictions, we need an average member-year-agency triad. The first table below shows the members who averaged 73, entered Congress between 2007 and 2011, were observed in our data for at least seven years, and most often submitted exactly one letter to an agency (the closest integer 1.29). For realism, this person would ideally, at some point in our data, become a chair. Of the modal legislators, Phil Roe meets this last criterion. The IRS is a fairly modal agency and one of the agencies to which Phil Roe submitted one letter in 2015, so predictions are at Phil Roe X IRS X 2015. Other legislators, years, and agencies are simply intercept shifts. 



```{r values, fig.width=5, fig.height=3}
modal <- dcounts_tenure %>% 
  group_by(icpsr) %>% 
  filter(first_year > 2006, first_year < 2013, max_year > 6) %>% 
  mutate(Chair = sum(chair, na.rm = T) >1) %>% 
  group_by(icpsr, year) %>%
  mutate(perLeg = sum(perYear)) %>% 
  filter(perYear == 1, perLeg == 73 ) %>% 
  select(perAgency = perYear, perLeg, icpsr, icpsr_agency, agency_year, first_year, max_year, Chair) %>% 
  distinct() %>% 
  ungroup() %>% left_join(members %>% select(bioname, icpsr))



modal %<>% filter(Chair)


# by chair and presidents' party
values <- tidyr::expand(dcounts_tenure,
                        agency = "Treasury_IRS",
                        chair = chair, 
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        first = FALSE,
                        second = FALSE,
                        third = FALSE,
                        fourth = FALSE,
                        fifth = FALSE, 
                        sixth = FALSE,
                        Legislator_x_Agency = "Treasury_IRS_20947",
                        Year_x_Agency = "Treasury_IRS_2015",
                        Legislator = "20947",
                        Year = "2015",
                        majority = TRUE,
                        presidents_party = presidents_party
                   ) %>% 
  drop_na(majority, chair)

# by year 
values_tenure <- tidyr::expand(dcounts_tenure,
                        agency = "Treasury_IRS",
                        chair = chair, 
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        first = first,
                        second = second,
                        third = third,
                        fourth = fourth,
                        fifth = fifth, 
                        sixth = sixth,
                        Legislator_x_Agency = "Treasury_IRS_20947",
                        Year_x_Agency = "Treasury_IRS_2015",
                        Legislator = "20947",
                        Year = "2015",
                        majority = TRUE,
                        presidents_party = TRUE
                   ) %>% 
  drop_na(chair)
```


# Simulated data

## Counts per legislator per agency per year

I replace the dependent variable, the count of letters that each legislator writes to each agency each year with a normal distribution with a mean 1 (the true mean in the data is 1.29). 

I also introduce a correlation with the calendar year by adding +1 for each year beyond 2007 (the first year in the data.) In this simulation 2017 would have a mean of 11. 

Later, I will introduce a correlation with tenure. (See "100 simulations section" below)


```{r echo = TRUE,  code_folding = "show"}
n <- nrow(dcounts_tenure)

sim <- dcounts_tenure %>% 
  # REPLACE DV WITH NORMAL DIST
  mutate(perYear = rnorm(n, year-2007)
         # OTHER VARS LEFT ALONE 
         # chair,
         # first,
         # second,
         # third,
         # fourth,
         # fifth,
         # sixth,
         # Year, 
         # Agency,
         # Legislator
  ) 

dcounts_tenure <- sim
```

---

# Models 

Our primary models are a series of difference-in-differences regressions that examine changes that are within legislator and agency pairs.

Estimates from Model 2 (Column 2 below) provides the estimated effects from the difference-in-differences specification. 

$Y_{ijt}  = {\beta}^{'} \textbf{Committee Position}_{it}  + \sum_{s = 1}^{6} \eta_{s} \text{I}\left(\text{tenure}_{it} = s\right) + \gamma_{ij} + \delta_{jt} + m_{it} + p_{it} + \epsilon_{ijt} $

Where $Y_{ijt}$ represents the number of requests legislator $i$ makes to agency $j$ in year $t$. Our analysis in this section is at the legislator-agency-year level. $\gamma_{ij}$ is a fixed effect for the legislator-agency pair. This fixed effect accounts for legislators' characteristics, such as legislators who are more skillful at filling constituency service requests than other legislators. Critically for our research design, this fixed effect also enables us to account for time-invariant constituent demands, ensuring differences in constituent demand do not drive our results. It also accounts for state and districts characteristics, including population, demographics, and local industries that might be particularly likely to request help with specific agencies. This difference-in-difference design ensures that coefficients ${\beta}$ capture variation related to changes in institutional power or experience, not other factors that may vary across districts, legislators, or agencies. The model also accounts for the different periods for which data were available from each agency. $\delta_{jt}$ is an agency-year fixed effect. This takes into account agency-level shocks that may affect legislator requests. 

Assuming that legislators' trends in the level of requests follow parallel paths, $\boldsymbol{\beta}$ represents the average effect of changing institutional power on a legislator's provision of constituency service.

In this same regression we also include indicators for legislators' first six years in Congress, $ \sum_{s = 1}^{6} \eta_{s} \text{tenure}_{it}$. The effects of interest $\eta_{1}, \eta_{2} : \eta_{6}$ describe how a legislator's provision of constituency service at levels of seniority between one and six years differ from legislators who serve beyond six years. We focus on constituency service levels in each of the first six years of a legislator's tenure to assess how constituency service changes over their initial years in Congress. This design allows us to assess the extent to which new legislators face start-up costs. 


# Estimation

Fixed effects general linear model `fixest::fixest`

```
feglm (perYear ~ 
 chair + ranking_minority + prestige +
 first + second + third + fourth + fifth + sixth + 
 majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
 cluster = "Legislator",
 data = dcounts_tenure)
```

Where

`perYear`  = $Y_{ijt}$ = Letters per legislator $i$ per agency $j$ per year $t$ 

`chair`= $\textbf{Committee Position}_{it}$ = Legislator $i$ is a committee chair in year $t$  

`first + second + third + fourth + fifth + sixth ` = $\text{I}\left(\text{tenure}_{it} = s\right)$ = Legislator i is in their $s$ (first, second, third, fourth, fifth, sixth) year of service in calendar year $t$

$\gamma_{ij}$ = a fixed effect for the legislator-agency pair =  `Legislator_x_Agency`

 $\delta_{jt}$ = an agency-year fixed effect = `Year_x_Agency`



---

# Counts per member per year

Clustering standard errors at the legislator level:

["Clustering on the panel variable produces an estimator of the VCE that is robust to cross-sectional heteroskedasticity and within-panel (serial) correlation that is asymptotically equivalent to that proposed by Arellano (1987)"](https://www.stata.com/manuals13/xtxtreg.pdf)

Replicated using `fixest::feglm` here and `xtreg` in Replication.do.
See more about robust (clustered) standard errors with fixed effects are calculated by `fixest` [here](https://lrberge.github.io/fixest/articles/standard_errors.html) and by  `xtreg` [here](https://www.stata.com/manuals13/xtxtreg.pdf).

```{r cm}
# Coef Map
cm = c("chair" = "Committee Chair",
       "ranking_minority" = "Ranking Member",
       "prestige" = "Prestige Committee",
       "first" = "First Year",
       "second" = "Second Year",
       "third" = "Third Year",
       "fourth" = "Fourth Year",
       "fifth" = "Fifth Year",
       "sixth" = "Sixth Year",
       "majority" = "Majority",
       "presidents_party" = "President's Party",
       "Legislator" = "Legislator", 
       "Agency" = "Agency",
       "FE: icpsr_agency" = "Legislator × Agency Fixed Effects",
       "icpsr_agency" = "Legislator × Agency Fixed Effects")

coef_omit = "(Intercept)|majority|presidents_party"
coef_omit = "none"

setFixest_dict(cm)

gof_omit = "R.*|AIC|BIC|Log.*|Std.*"

# table formatting to match stata (sort of)
format_table <- . %>% 
  row_spec(row = 1, bold = T, hline_after = TRUE) %>% 
      kable_styling(font_size = 11) %>% 
                    #full_width = TRUE, 
                    #latex_options = c("repeat_header")) %>%
  str_replace("Num.Obs.", "Observations") %>% 
  str_replace("Std.Errors", "Robust/Clustered Std. Errors") %>% 
  str_replace("FE: Legislator_x_Agency", "Legislator x Agency FE") %>%
  str_replace("FE: Year_x_Agency", "Year x Agency FE") %>% 
  str_replace("FE: Year", "Year Fixed Effects") %>% 
  str_replace("FE: Legislator", "Legislator Fixed Effects") %>%
    str_replace_all("X|✓", "\\\\\\checkmark") %>% 
  # a random midrule appeared in the wrong place 
  #str_remove("\\midrule") %>% 
  #  extract just the table, no caption etc
  str_extract("\\\\begin\\{tabular\\}(\n|.)*tabular\\}") 
```


---




## Total Letters 

### Coeficient Plots

- Figures: `figs/m-total-[1:4].png`

1. "cross-sectional"
2. "diff-in-diff"
3. "cross-sectional re-elected"
4. "diff-in-diff re-elected"

```{r m-total-sim,  fig.show="hold", out.width="50%", fig.height=4.5, fig.cap= "Total Letters Per Year", fig.subcap= c("cross-sectional","diff-in-diff","cross-sectional re-elected","diff-in-diff re-elected")}
testing = F

# paper table 
# 1 
# cross-sectional 
m_total_cross <-feglm (perYear ~ 
                         chair + ranking_minority + prestige + 
                    first + second + third + fourth + fifth + sixth + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = dcounts_tenure)

if(testing){modelsummary(m_total_cross, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_total_cross, horiz = T, drop = "(Intercept)") 



# 2
m_total_dnd <-feglm (perYear ~ 
                       chair + ranking_minority + prestige + 
                    first + second + third + fourth + fifth + sixth + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = dcounts_tenure)

if(testing){modelsummary(m_total_dnd, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_total_dnd, horiz = T) 


# 3
m_total_2nd <-feglm (perYear ~ 
                       chair + ranking_minority + prestige + 
                    first + second + third + fourth + fifth + sixth + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator", 
           data = dcounts_tenure %>% filter(survive == 1))

if(testing){modelsummary(m_total_2nd, gof_omit = "R.*", coef_omit = coef_omit)}
coefplot(m_total_2nd, horiz = T) 


# 4
m_logtotal_dnd <-feglm (log(perYear + 1) ~ 
                          chair + ranking_minority + prestige + 
                    first + second + third + fourth + fifth + sixth + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator", 
           data = dcounts_tenure)

if(testing){modelsummary(m_logtotal_dnd, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_logtotal_dnd, horiz = T) 


```

### Total Letters Table 

- Table: `tables/models_total.tex` (sans stars)


```{r models_total}
models_total <- list(
  "(1)" = m_total_cross,
  "(2)" = m_total_dnd,
  "(3)" =  m_total_2nd,
  "(4)" = m_logtotal_dnd
)

rows <- tibble(
  term = c("Dependent Variable", 
           "Majority",
           "President's Party",
           "All Legislators", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "✓", "✓", "✓", ""),
  `(2)` =c("Count", "✓", "✓", "✓", ""),
  `(3)` = c("Count", "✓","✓","", "✓"),
  `(4)` = c("Log(Count+1)","✓","✓", "✓", "") 
)

rows <- tibble(
  term = c("Dependent Variable", 
           #"Majority",
           #"President's Party",
           "All Legislators", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "✓", ""),
  `(2)` =c("Count", "✓", ""),
  `(3)` = c("Count","", "✓"),
  `(4)` = c("Log(Count+1)", "✓", "") 
)

# subset
attr(rows, 'position') <- c(0, 20,21,22,23)

# call coefs
attr(rows, 'position') <- c(0, 24,25)


# HTML
modelsummary(models_total, stars = T, 
             add_rows = rows, 
             coef_map = cm,
             gof_omit = gof_omit,
             coef_omit = coef_omit,
             title = "The Effect of Expierence and Institutional Power on Legislator Contacts", 
             notes = list("Robust standard errors in parentheses, clustered by legislator.")) %>% row_spec(row = 1, bold = T, hline_after = TRUE) 

# TeX 
modelsummary(models_total, # stars = T, 
             add_rows = rows,               
             coef_map = cm, 
             gof_omit = gof_omit, 
             coef_omit = coef_omit,
             output = "latex",
             #title = "\\\\footnotesize The Effect of Expierence and Institutional Power on Legislator Contacts", 
             notes = list("\\\\footnotesize Robust standard errors in parentheses, clustered by legislator.")) %>% 
  format_table() %>%
  write_lines(file = here::here("docs", "tables", "models_total.tex") )


beta <- m_total_dnd$coefficients %>%
  round(3) %>% 
  as_tibble(rownames = "beta") %>% 
  pivot_wider(names_from = beta)

se <- m_total_dnd$se %>%
  round(3) %>% as_tibble(rownames = "se") %>%
  pivot_wider(names_from = se)
```



### Total Letters Predictions 

- Figures: `figs/m-total-predicted-[1:4].png`



```{r}
# helper functions to plot predicted values
ggchair <- function(predicted = predicted) {
  
  predicted$chair %<>% str_replace("0", "Not Chair") %>% str_replace("1", "Chair")
  
  predicted$presidents_party %<>% str_replace("0", "Not President's Party") %>% str_replace("1", "President's Party")

predicted %>%  
  ggplot() + 
  aes(x = "", 
      y = estimate, 
      fill = chair,
      shape = chair,
      color = chair,
      ymin = conf.low,
      ymax = conf.high) + 
  geom_pointrange(position =  position_dodge(width = -.5)  )  + 
  scale_fill_viridis_d(begin = 0, end = .6, option = "cividis") +
  scale_color_viridis_d(begin = 0, end = .6, option = "cividis") +
      theme_minimal() + 
  theme(panel.border  = element_blank(),
        panel.grid.major.x = element_blank()) + facet_grid(. ~ presidents_party) 
}


ggtenure <- function(predicted = predicted) {
  
predicted %<>%
  # drop estimates from impossible values
      group_by(rowid, estimate, conf.low, conf.high, chair) %>% 
  mutate(sum = sum(first, second, third, fourth, fifth, sixth),
         more = ifelse(sum == 0, 1,0)) %>% 
    filter(sum < 2) %>% 
    pivot_longer(cols = c("first", "second", "third", "fourth", "fifth", "sixth", "more")) %>% 
    select(name, value) %>% 
    filter(value == 1) %>% 
    # clean up for presentation
    mutate(year_in_congress = name %>% 
             str_replace("more", "7\nor more") %>% 
             str_replace("sixth", "6") %>% 
             str_replace("fifth", "5") %>% 
             str_replace("fourth", "4") %>% 
             str_replace("third", "3") %>% 
             str_replace("second", "2") %>% 
             str_replace("first", "1") 
             ) %>% 
    ungroup()
  
# Ideally, we could plot against data, but there is so much variation that you can no longer distinguish differences in predicted values 
# predicted %<>% full_join(dcounts_tenure2 %>% mutate(predicted = NA))
  
predicted %<>% filter(chair == 0 | name %in% c("sixth", "more"))

  predicted$chair %<>% str_replace("0", "Not Chair") %>% str_replace("1", "Chair")
  

predicted %>%  
  ungroup() %>% 
  ggplot() + 
  aes(x = year_in_congress, 
      y = estimate, 
      shape = chair,
      color = chair,
      ymin = conf.low,
      ymax = conf.high) + 
  geom_pointrange(position =  position_dodge(width = -.3)  )  + 
  scale_fill_viridis_d(begin = 0, end = .6, option = "cividis") +
  scale_color_viridis_d(begin = 0, end = .6, option = "cividis") +
      theme_minimal() + 
  theme(panel.border  = element_blank(),
        panel.grid.major.x = element_blank()) 
  
}

```


```{r m-total-predicted-sim,  fig.show="hold", out.width="50%", fig.cap= "Total", fig.subcap= c("1","2","3","4")}
predicted <- predictions(m_total_cross,
                         newdata = values)

# Cross-sectional predictions
predicted %>%
    mutate(estimate = estimate*90,
         conf.low = conf.low*90, 
           conf.high = conf.high*90) %>%
  ggchair() + 
  labs(title = "Predicted Total Letters per Year\n(Cross-Sectional)",
       x = "",
       y = "Predicted Total Letters Per Year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted <- predictions(m_total_cross,
                         newdata = values_tenure)

predicted %>%
    mutate(estimate = estimate*90,
         conf.low = conf.low*90, 
           conf.high = conf.high*90) %>% 
ggtenure() +
  labs(title = "Predicted Total Letters Per Year\n(Cross-Sectional)",
       x = "Years Serving in Congress",
       y = "Predicted Letters Per Year",
       fill = "",
       color = "",
       shape = "") 


# diff in diff 
predicted <- predictions(m_total_dnd,
                         newdata = values)


# predictions by chair and presidents' party
predicted %>%
    mutate(estimate = estimate*90,
           conf.low = conf.low*90, 
           conf.high = conf.high*90) %>%
  ggchair() + 
  labs(title = "Predicted Total Letters per Year\nDifference in Differences (Within-Legislator)",
       x = "",
       y = "Predicted Letters Per Year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted <- predictions(m_total_dnd,
                         newdata = values_tenure)

predicted %>%
    mutate(estimate = estimate*90,
           conf.low = conf.low*90, 
           conf.high = conf.high*90) %>%
ggtenure() +
    geom_line(aes(x = as.numeric(year_in_congress %>% str_sub(1,1)))) + 
  labs(title = "Predicted Total Letters Per Year\nDifference in Differences (Within-Legislator)",
       x = "Years Serving in Congress",
       y = "Predicted Letters Per Year",
       fill = "",
       color = "",
       shape = "") 
```


# 100 simulations

Subletting data to legislators in their first 6 years and setting the mean of the simulated DV (letters per legislator per year per agency) to their year (tenure) in office. 

```{r sims}
# A function to estimate diff in diff with a new random sample for DV 
sim_data <- dcounts_tenure %>% filter(tenure<7, tenure>0)

if(FALSE){
icpsr <- 1:500
years <- 2010:2020
  
sim_data <- expand_grid(icpsr, years) %>% 
  # REPLACE DV WITH NORMAL DIST
  group_by(icpsr) %>%
  mutate(perYear = rnorm(n, tenure),
         year_elected = runif(n, 2000, 2020),
         tenure = year - yearelected,
         chair = runif(n, 0,1),
         chair = ifelse(tenure>6, chair, 0)
         ) %>% 
    # remove impossible values
    filter(yearelected <= year)
           
         # chair,
         # first,
         # second,
         # third,
         # fourth,
         # fifth,
         # sixth,
         # Year, 
         # Agency,
         # Legislator
# sim_data$tenure
}
```


## Cross sectional


```{r sim-cross}
simulation_cross <- function(x){
  
  set.seed(x)
  
  data <- sim_data %>% 
  # REPLACE DV WITH NORMAL DIST
  mutate(perYear = rnorm(n, tenure)) # year-2007))

m_total <-feglm (perYear ~ 
                       #chair + ranking_minority + prestige + 
                    first + second + third + fourth + fifth + sixth | Year_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data)

beta <- m_total$coefficients %>%
  #round(3) %>% 
  as_tibble(rownames = "beta") %>% 
  pivot_wider(names_from = beta)

return(beta)
}

# run 100 times 
sims <- map_dfr(.x = 1:100, .f =  simulation_cross)

# # plot estimates
# sims %>% 
#   ggplot() +
#   aes(x = first) + 
#   geom_density(fill = "grey")  #+  geom_vline(xintercept = 1)

sims %>% 
  ggplot() +
  aes(x = second) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = third) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = fourth) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = fifth) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = sixth) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)
```



## Diff in diff 

```{r sim-dnd}
simulation_dnd <- function(x){
  
  set.seed(x)
  
  data <- sim_data %>% 
  # REPLACE DV WITH NORMAL DIST
  mutate(perYear = rnorm(n, tenure)) # year-2007))

m_total_dnd <-feglm (perYear ~ 
                      # chair + ranking_minority + prestige + 
                      # majority + presidents_party 
                      first + second + third + fourth + fifth + sixth | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data)

beta <- m_total_dnd$coefficients %>%
  #round(3) %>% 
  as_tibble(rownames = "beta") %>% 
  pivot_wider(names_from = beta)

return(beta)
}

# run 100 times 
sims <- map_dfr(.x = 1:100, .f =  simulation_dnd)

# plot estimates
# sims %>% 
#   ggplot() +
#   aes(x = first) + 
#   geom_density(fill = "grey")  #+  geom_vline(xintercept = 1)

sims %>% 
  ggplot() +
  aes(x = second) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = third) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = fourth) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = fifth) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)

sims %>% 
  ggplot() +
  aes(x = sixth) + 
  geom_density(fill = "grey") #+ geom_vline(xintercept = 2)
```


## Reviewer simulation code 

```
matrix B = J(1000, 7, .)
matrix colnames B = exp1 exp2 exp3 exp4 exp5 exp6 chair
       
qui forval j = 1/1000 {
       
       

        *first create 500 districts observed over 10 time periods
        clear
        set obs 500
        gen dist_id = _n
        //make time periods
        expand 10
        bys dist_id: gen time = _n
       
        *Next, create legislators in each district (entering and exiting at different times)
        gen random = runiform()
        bys dist_id: gen new_elected = random>0.75 | _n==1 // randomly determine when legislators are kicked out
        bys dist_id new_elected (time) : gen leg_number = _n if new_elected==1 // generate a number of each legislator
        drop random new_elected
        sort dist_id time
        bys dist_id: replace leg_number = leg_number[_n-1] if leg_number==. &  leg_number[_n-1]!=. // assign number to each legislator
        egen dist_leg_id = group(dist_id leg_number) // make legislator-district id


       
        *create variables
        bys dist_leg_id (time): gen experience = _n // create experience for each legislator
       
        bys dist_leg_id: egen quality = max(experience) // fixed legislator quality, positive correlation between quality and experience
       

        gen chair = 0
        replace chair =1 if  runiform()>0.5 & experience>3
       
        *create outcome: additive separability: quality, experience, chair and time
        gen outcome = quality + experience + chair + time +rnormal(0,1)
       
        gen experience_firstsix = experience
        replace experience_firstsix = 0 if experience>6 // set reference category to experience in year 7 and more
       
       
        ** run regression
        areg outcome chair i.experience_firstsix i.time, absorb(dist_leg_id )  // the diff-in-diff identifies the effect of chair, but not the effect of experience

        *store point estimates
        forval v=1/6 {
                matrix B[`j', `v'] = _b[`v'.experience_firstsix]
        }
        matrix B[`j', 7] = _b[chair]
       
}      

matrix list B
clear
svmat B, names(matcol)
collapse B*
```
